rbeast2: BEAUti 2, BEAST2 and Tracer for R

### 2018-02-20 article.tex
Fig at end of paper

BEAUti, and likewise \verb;rbeast2;, needs at least a FASTA filename
to produce a BEAST2 configuration file. 
In BEAUti, this is achieved by loading a FASTA file, 
then saving an output file using a common
save file dialog. After this, BEAST2 needs to be invoked
on the created configuration file to create multiple files
storing the posterior created by BEAST2. Finally, these output
files must be parsed by either Tracer of DensiTree.

In \verb;rbeast2;, the same is achieved by:

@@

\begin{lstlisting}[language=R, floatplacement=H]
out <- run_beast2(
  "alignment.fas",
  tree_priors = create_yule_tree_prior(
    birth_rate_distr = create_exp_distr()    
  )
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=H]
out <- run_beast2(
  "alignment.fas",
  posterior_crown_age = 15
)
\end{lstlisting}

>>>>

BEAUti, and likewise \verb;rbeast2;, needs at least a FASTA filename
to produce a BEAST2 configuration file. 
In BEAUti, this is achieved by loading a FASTA file, 
then saving an output file using a common
save file dialog. After this, BEAST2 needs to be invoked
on the created configuration file to create multiple files
storing the posterior created by BEAST2. Finally, these output
files must be parsed by either Tracer of DensiTree.
In \verb;rbeast2;, the same is achieved by:

@@

\begin{lstlisting}[language=R, floatplacement=H]
out <- run_beast2(
  "anthus_aco.fas",
  tree_priors = create_yule_tree_prior(
    birth_rate_distr = create_exp_distr()    
  )
)
\end{lstlisting}

Within this same example, one may specify
the initial shape parameters of the exponential distribution.
In BEAST2's implementation, an exponential distribution 
has one shape parameter: its mean, which can be set to any
value with \verb;BEAUti;. Within \verb;rbeast2;, to set the 
initial mean value of the exponential distribution, do:

\begin{lstlisting}[language=R, floatplacement=H]
out <- run_beast2(
  get_path("anthus_aco.fas"),
  tree_priors = create_yule_tree_prior(
    birth_rate_distr = create_exp_distr(
      mean = create_mean_param(value = 1.0)
    )    
  )
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=H]
out <- run_beast2(
  "anthus_aco.fas",
  posterior_crown_age = 15
)
\end{lstlisting}
